Combining bottom up and top down approaches for Drug-Target-Interaction prediction

### 2019-12-08 presentations/2019-12-09/presentation.tex
Rerun different embeddings 1, added presentation

\definecolor{myblue}{RGB}{80,80,160}
\definecolor{mygreen}{RGB}{80,160,80}
\definecolor{myturk}{RGB}{160,160,160}

@@

	\begin{tikzpicture}[thick,
	every node/.style={draw,circle},
	fsnode/.style={fill=myblue},
	fs1node/.style={fill=myturk},
	ssnode/.style={fill=mygreen},
	%every fit/.style={ellipse,draw,inner sep=-1pt,text width=2cm},
	%->,shorten >= 3pt,shorten <= 3pt
	]

@@

\section{Recent approaches}
\begin{frame}{Classification of recent approaches\footnote{Chen Wang et al., Briefings in Bioinformatics, 2018}\footnote{Yu Ding, Briefings in Bioinformatics, 2019}}
	\begin{table}
		\begin{tabularx}{\textwidth}{|>{\setlength\hsize{.5\hsize}\setlength\linewidth{\hsize}}X|>{\setlength\hsize{1.25\hsize}\setlength\linewidth{\hsize}}X|>{\setlength\hsize{1.25\hsize}\setlength\linewidth{\hsize}}X|}
			\hline
			&Drugs&Protein\\
			\hline
			bottom-up&
			\begin{itemize}
				\item GCN over molecules
				\item drug similarity
			\end{itemize}&
			\begin{itemize}
				\item secondary structure prediction
				\item contact prediction
				\item convolution over amino acid sequences
			\end{itemize}\\
			\hline
			top-down&
			\begin{itemize}
				\item network approaches
				\item drug similarity
			\end{itemize}&
			\begin{itemize}
				\item protein similarity
			\end{itemize}\\
			\hline
		\end{tabularx}
	\end{table}	
\end{frame}

\begin{frame}{Problems of recent approaches}
	Main issues:
	\begin{itemize}
		\item lack of generalization
		\item Usually only top-down or bottom-up
	\end{itemize}
	\pause
	\begin{tikzpicture}[thick,
	every node/.style={draw,circle},
	fsnode/.style={fill=myblue},
	fs1node/.style={fill=myturk},
	ssnode/.style={fill=mygreen},
	%every fit/.style={ellipse,draw,inner sep=-1pt,text width=2cm},
	%->,shorten >= 3pt,shorten <= 3pt
	]

@@

@@

>>>>

\definecolor{myblue}{RGB}{80,80,160}
\definecolor{mygreen}{RGB}{80,160,80}
\definecolor{myturk}{RGB}{240,60,60}

@@

	\begin{tikzpicture}[thick,
	every node/.style={draw,circle},
	fsnode/.style={fill=myblue},
	fs1node/.style={fill=myblue},
	ssnode/.style={fill=mygreen},
	%every fit/.style={ellipse,draw,inner sep=-1pt,text width=2cm},
	%->,shorten >= 3pt,shorten <= 3pt
	]

@@

\section{Recent approaches}
\begin{frame}{Classification of recent approaches\footnote{Chen Wang et al., Briefings in Bioinformatics, 2018}\footnote{Yu Ding et al., Briefings in Bioinformatics, 2019}}
	\begin{table}
		\begin{tabularx}{\textwidth}{|>{\setlength\hsize{.5\hsize}\setlength\linewidth{\hsize}}X|>{\setlength\hsize{1.25\hsize}\setlength\linewidth{\hsize}}X|>{\setlength\hsize{1.25\hsize}\setlength\linewidth{\hsize}}X|}
			\hline
			&Drugs&Protein\\
			\hline
			bottom-up&
			\begin{itemize}
				\item GCN over molecules
				\item drug similarity
			\end{itemize}&
			\begin{itemize}
				\item secondary structure prediction
				\item contact prediction
				\item convolution over amino acid sequences
			\end{itemize}\\
			\hline
			top-down&
			\begin{itemize}
				\item network approaches
				\item drug similarity
			\end{itemize}&
			\begin{itemize}
				\item protein similarity
			\end{itemize}\\
			\hline
		\end{tabularx}
	\end{table}	
\end{frame}

\begin{frame}{Problems of recent approaches}
	Main issues:
	\begin{itemize}
		\item Lack ability to generalize or are unable to spot small differences
		\item Usually only top-down or bottom-up
		\item Not making use of interaction networks
	\end{itemize}
	\pause
	\begin{tikzpicture}[thick,
	every node/.style={draw,circle},
	fsnode/.style={fill=myblue},
	fs1node/.style={fill=myturk},
	trainlegendnode/.style={fill=myblue},
	testlegendnode/.style={fill=myturk},
	ssnode/.style={fill=mygreen},
	%every fit/.style={ellipse,draw,inner sep=-1pt,text width=2cm},
	%->,shorten >= 3pt,shorten <= 3pt
	]

@@

	% legend
	\begin{scope}[xshift=7cm,yshift=-0.25cm,start chain=going below,node distance=7mm]
	\foreach \i in {1}
	\node[trainlegendnode,on chain] (trainlegend\i) [label=right: Train] {};
	\end{scope}

	\begin{scope}[xshift=7cm,yshift=-0.25cm, node distance=1mm]
	\foreach \i in {1}
	\node[testlegendnode,on chain] (testlegend\i) [label=right: Test] {};
	\end{scope}

@@

\begin{frame}{}
